---
title       : 
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Project Overview

The Shiny App shows the climate variables collected in New york City. Users can filter to see the barplots by either the month or the 
climate variable (Ozone,Solar.R,Wind,Temp)

---
## Details

Quoted from R's documentation when 
```{r,echo=FALSE,eval=FALSE}
?airquality
```
Daily readings of the following air quality values for May 1, 1973 (a Tuesday) to September 30, 1973.
-Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island
-Solar.R: Solar radiation in Langleys in the frequency band 4000-7700 Angstroms from 0800 to 1200 hours at Central Park
-Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport
-Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.

---
## Data set Overview

Here is the overview of the dataset.

```{r , echo=FALSE}
head(airquality)
summary(airquality)
```

---
## Errors Made

- Usuage of reactive functions were neccessary.

---
## Conclusion
- Writing a simple application like this, can help to reduce repetive tasks.
- Putting it on a webpage, literally opens up this application to anyone (even layman) to be able to use R functions.




